MS Prelim Data K23

### 2024-07-12 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
Add files via upload

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(stringr)
library(MatchIt)
#functions
source("~/BBL/msanxiety/scripts/ms_functions.R")
```

@@

## Anxiety burden severity T test ranking

@@

###Collapse anxiety dx and antianxiety meds with those plus depression
```{r group_anxietydx_meds_and_dep_comorbidity}

@@

df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oAnxietydx.Meds.Inc.Dep.Collapsed != "unclassified") %>%
  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxietydx.Meds.Inc.Dep.Collapsed, osex)

 tibble_overall_summaries <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
tibble_overall_summaries

tibble_overall_summaries_by_sex <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed, osex) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_by_sex

  tibble_overall_summaries_females <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  filter(osex == "Female") %>%
  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_females

    tibble_overall_summaries_males <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  filter(osex == "Male") %>%
  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_males

  #mean disease
  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_mean_disease_lm)

  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_by_sex_mean_disease_lm)

  #anxiety network
  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_anxiety_net_lm)

  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_by_sex_anxiety_net_lm)

  #UF R
  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_R_lm)

  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_R_by_sex_lm)

  #UF L
  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_L_lm)

  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_L_by_sex_lm)

  #burden of anxiety by network
  #clean up data frame
  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed != "unclassified") %>%
  filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.anxietydx")) %>%  #-> doesn't work
 # filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "On.Anxiolytics")) %>% #-> doesn't work
  mutate(subject = as.factor(EMPI)) %>%
#  mutate(Diagnosis = oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
  mutate(Diagnosis = ifelse(oAnxietydx.Meds.Inc.Dep.Collapsed=="healthy_ish", "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  #mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
  #mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
  #mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
  ##mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
  #mutate(Benzo_status = as.factor(Benzo_status)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

@@

#mean = 0.4911045
mean_nonanxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
mean_nonanxiety_dx_anx_net

#mean = 0.2544921
mean_nonanxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
mean_nonanxiety_dx_nonanx_net

 #simple lmer, NetworkNonanxiety_network  -0.241926   0.003943 661.000022  -61.36   <2e-16 ***
disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)

#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
```

### Plot within vs outside network
```{r plottting_bar_graph}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(stringr)
library(MatchIt)
library(ggpubr)
#functions
source("~/BBL/msanxiety/scripts/ms_functions.R")
```

@@

## Anxiety burden severity ranking

@@

#### plots
```{r}
  #proportion injured over whole brain
prop_injured_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_per_total_network_size_sum, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_by_anxiety_burden_plot

  #proportion injured over anxiety net
prop_injured_anxiety_net_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_anxiety_net_by_anxiety_burden_plot

  #proportion injured over nonanxiety net
prop_injured_nonanxiety_net_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_nonanxiety_net_by_anxiety_burden_plot

  #proportion injured over R Uncinate prop
prop_injured_R_uncinate_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=UF_R_prop, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_R_uncinate_by_anxiety_burden_plot

  #proportion injured over L Uncinate prop
prop_injured_L_uncinate_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=UF_L_prop, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_L_uncinate_by_anxiety_burden_plot

prop_injured_by_anxiety_burden_and_sex_plot <- ggboxplot(df_disease_burden_unc_and_anx_net, x = "oAnxiety.And.Dep.And.AnxietyMedsGroupVar", y = "proportion_volume_lost_per_total_network_size_sum", color = "osex",
          palette = c("#00AFBB", "#E7B800")) +
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_by_anxiety_burden_and_sex_plot

#Anxiety network interactions and uncinate alone, TRUE HEALTHY
```{r anxiety_net_intx}

make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified",])

#clean up data frame
cleaned_df <- df_demo_and_fascicles %>%
  filter(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified") %>% #lose 93, n now 719
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  mutate(mean_uncinate_injury = (UF_L_prop + UF_R_prop)/2) %>%
  mutate(mean_uncinate_and_fornix_injury = (UF_L_prop + UF_R_prop + F_R_prop + F_L_prop)/2) %>%
  ungroup()

## Anxiety burden severity ranking true healthy

I am wondering here if, as my brain wants to think, that things in the chart reflect severity of anxiety. For example, I'd expect people with dep and anxiety comorbidity and on meds would be the sickest, followed by anxiety + on meds, then on meds, then anxiety dx, then healthyish. I am going to do a t-test comparing proportion of disease over whole brain, over anxiety net, and over uncinate in each of those groups as compared to the healthy group, and rank the T to see if that pattern bears out. And if it does, do some sort of regression.
```{r anxiety_burden_severity_ranking }
#variables_to_evaluate <- c("Has.Anxietydx.AND.AntianxietymedGroupVar")
df_disease_burden_unc_and_anx_net_true_healthy <- df_demo_and_fascicles %>%
  filter(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified") %>%
  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, osex)

tibble_n <- df_disease_burden_unc_and_anx_net_true_healthy %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>% 
  summarise(n())

tibble_overall_disease <- 
  df_disease_burden_unc_and_anx_net_true_healthy %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
  summarize(mean_size = mean(proportion_volume_lost_per_total_network_size_sum))

tibble_overall_summaries <- 
  df_disease_burden_unc_and_anx_net_true_healthy %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
tibble_overall_summaries

tibble_overall_summaries_by_sex <- 
  df_disease_burden_unc_and_anx_net_true_healthy %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, osex) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_by_sex

  tibble_overall_summaries_females <- 
  df_disease_burden_unc_and_anx_net_true_healthy %>% 
  filter(osex == "Female") %>%
  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_females

    tibble_overall_summaries_males <- 
  df_disease_burden_unc_and_anx_net_true_healthy %>% 
  filter(osex == "Male") %>%
  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_males

#### plots
```{r}
  #proportion injured over whole brain
prop_injured_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=proportion_volume_lost_per_total_network_size_sum, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_by_anxiety_burden_true_healty_plot

  #proportion injured over anxiety net
prop_injured_anxiety_net_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_anxiety_net_by_anxiety_burden_true_healty_plot

  #proportion injured over nonanxiety net
prop_injured_nonanxiety_net_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_nonanxiety_net_by_anxiety_burden_true_healty_plot

  #proportion injured over R Uncinate prop
prop_injured_R_uncinate_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=UF_R_prop, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_R_uncinate_by_anxiety_burden_true_healty_plot

  #proportion injured over L Uncinate prop
prop_injured_L_uncinate_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=UF_L_prop, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_L_uncinate_by_anxiety_burden_true_healty_plot

prop_injured_by_anxiety_burden_and_sex_true_healty_plot <- ggboxplot(df_disease_burden_unc_and_anx_net_true_healthy, x = "oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar", y = "proportion_volume_lost_per_total_network_size_sum", color = "osex",
          palette = c("#00AFBB", "#E7B800")) +
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_by_anxiety_burden_and_sex_true_healty_plot

##Collapse anxiety dx and antianxiety meds with those plus depression
```{r group_anxietydx_meds_and_dep_comorbidity}

@@

df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)

 tibble_overall_summaries <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
tibble_overall_summaries

tibble_overall_summaries_by_sex <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_by_sex

  tibble_overall_summaries_females <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  filter(osex == "Female") %>%
  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_females

    tibble_overall_summaries_males <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  filter(osex == "Male") %>%
  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_males

  #mean disease
  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_mean_disease_lm)

  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_by_sex_mean_disease_lm)

  #anxiety network
  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_anxiety_net_lm)

  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_by_sex_anxiety_net_lm)

  #UF R
  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_R_lm)

  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_R_by_sex_lm)

  #UF L
  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_L_lm)

  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_L_by_sex_lm)

  #burden of anxiety by network
  #clean up data frame
  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
  #filter(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed == c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.anxietydx")) %>%  #-> doesn't work
 # filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "On.Anxiolytics")) %>% #-> doesn't work
  mutate(subject = as.factor(EMPI)) %>%
#  mutate(Diagnosis = oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
  mutate(Diagnosis = ifelse(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  #mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
  #mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
  #mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
  ##mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
  #mutate(Benzo_status = as.factor(Benzo_status)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

@@

#mean = 0.4762486
mean_nonanxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
mean_nonanxiety_dx_anx_net

#mean = 0.2444919
mean_nonanxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
mean_nonanxiety_dx_nonanx_net

 #simple lmer, NetworkNonanxiety_network   -0.23176    0.01462 85.00000 -15.855   <2e-16 ***; NetworkNonanxiety_network:DiagnosisMS+Anxiety -0.03822    0.02241 85.00000  -1.705   0.0918 .
disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)

#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)

#do anova instead

disease_within_vs_outside_anxiety_net_by_dx_groups_anova <- aov(proportion_affected ~ Network+Diagnosis + Network:Diagnosis, data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_by_dx_groups_anova)

#do lm UF*Diagnosis
 #UF_R_vol -> NS
disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis, data = df_empi_dx_network_proportions)
summary(disease_UF_R_vol_lm)

 #UF_L_vol -> NS
disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis, data = df_empi_dx_network_proportions)
summary(disease_UF_L_vol_lm)

###plots
```{r}
prop_injured_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x= oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed , y=proportion_volume_lost_per_total_network_size_sum, fill= oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed )) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_by_anxiety_burden_collapsed_vars_plot

  #proportion injured over anxiety net
prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot
